GravExplain: Continuous gravitational wave data analysis in a table-top experiment

### 2020-01-31 paper/paper_main.tex
62nd day of Summer

\section{Circuit design}
% schematic of breadboard and connections to pi
% https://www.circuit-diagram.org/editor/

>>>>

\section{Circuit design}
% schematic of breadboard and connections to pi
% https://www.circuit-diagram.org/editor/
% https://crcit.net/c/e397dcc2166943d69155f9dac1e27bce

\begin{figure}
	\includegraphics[width=\textwidth]{circuit_diagram.pdf}
	\caption{Circuit diagram for photo-diode reading. Photo-diode in reverse-bias over an op-amp, analog signal then passed through Sallen-Key anti-aliasing filter tuned to 16kHz, then into an analog-to-digital converter (ADC), that’s finally read by the special purpose input (SPI) pins of a Raspberry Pi}
	\label{fig:circuit_diagram}
\end{figure}
